Distributional Trees and Forests

### 2017-06-28 pkg/disttree/inst/useR2017/slides.Rnw
changed yscale of the density plot and added Heidi as coauthor on the title slide
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/partykit@1498 255f4249-2263-4417-b1ea-8498779e27a7

\title{Distributional Trees and Forests}
\author{Lisa Schlosser, Torsten Hothorn, Achim Zeileis}
\URL{http://R-Forge.R-project.org/projects/partykit}
\Conference{useR! 2017}
\date{2017-07-05}

@@

\begin{frame}[fragile]
\frametitle{Fitting a Tree}
\begin{center}
\vspace*{-0.12cm}
Model: \code{disttree(y ~ x)}\\
\vspace*{-0.2cm}
\setkeys{Gin}{width=0.68\linewidth, height=0.68\linewidth}
<<plottree_dens, fig=TRUE, echo=FALSE>>=
node_density <- function (tree, xscale = NULL, yscale = NULL, horizontal = FALSE,
                          main = "", xlab = "", ylab = "Density", id = TRUE, rug = TRUE,
                          fill = paltrees[c(1, 3)], col = "black", lwd = 0.5, ...) 
{
  yobs <- tree$data[,as.character(tree$info$formula[[2]])]
  ylines <- 1.5
  if (is.null(xscale)) xscale <- c(-5.1,22.5)
  if (is.null(yscale)) yscale <- c(-0.05,0.5)
  xr <- xscale
  yr <- yscale

>>>>

\title{Distributional Trees and Forests}
\author{Lisa Schlosser, Torsten Hothorn, \\
Heidi Seibold, Achim Zeileis}
\URL{http://R-Forge.R-project.org/projects/partykit}
\Conference{useR! 2017}
\date{2017-07-05}

@@

\begin{frame}[fragile]
\frametitle{Fitting a Tree}
\begin{center}
\vspace*{-0.12cm}
Model: \code{disttree(y ~ x)}\\
\vspace*{-0.2cm}
\setkeys{Gin}{width=0.68\linewidth, height=0.68\linewidth}
<<plottree_dens, fig=TRUE, echo=FALSE>>=
node_density <- function (tree, xscale = NULL, yscale = NULL, horizontal = FALSE,
                          main = "", xlab = "", ylab = "Density", id = TRUE, rug = TRUE,
                          fill = paltrees[c(1, 3)], col = "black", lwd = 0.5, ...) 
{
  yobs <- tree$data[,as.character(tree$info$formula[[2]])]
  ylines <- 1.5
  if (is.null(xscale)) xscale <- c(-5.1,22.5)
  if (is.null(yscale)) yscale <- c(-0.05,0.45)
  xr <- xscale
  yr <- yscale
